\bf Faster Neural Machine Translation Inference

### 2018-02-09 fast-beam/fast-beam.tex
fast beam paper

Simpler, faster models have been created that are as good, or almost as good, as more slower, more complex models~\citep{DBLP:journals/corr/BahdanauCB14}. Research have also gone into smaller, faster models that can approximate the original, slower, bigger model~\citep{DBLP:conf/emnlp/KimR16}. Some models have been justified as more suited for the parallel architecture of GPUs~\cite{DBLP:journals/corr/VaswaniSPUJGKP17}.

>>>>

Simpler, faster models have been created that are as good, or almost as good, as more slower, more complex models~\citep{DBLP:journals/corr/BahdanauCB14}. Research have also gone into smaller, faster models that can approximate slower, bigger models~\citep{DBLP:conf/emnlp/KimR16}. Some models have been justified as more suited for the parallel architecture of GPUs~\cite{DBLP:journals/corr/VaswaniSPUJGKP17}~\cite{gehring2017convs2s}.
